Population genetic reconstruction of mutation spectrum evolution from unphased genomes

### 2019-12-03 manuscript/main.tex
non-identifiability of N(t) mu(t)

>>>>

\subsection*{Non-identifiability of demographic history and total mutation rate}

As shown in appendix \ref{sec:appendix:forward:pcsws} eqn~\eqref{eqn:d2}, $\eta(t)$ and $\mu(t)$ are non-identifiable at all times.
This is shown by introducing a change of variables that measures time in expected number of coalescent events since the present.
This non-identifiability is similarly manifest by a change of variables to measure time in expected mutations \citetext{Peter Ralph, priv.\ comm., 2019}.
